---
title: "Analysis on mpg in mtcars"
output: word_document
---

##Summary
This is an analysis on mtcars, main goal is to see the impact to mpg from transmission type (Auto vs Manual)

##Exploratory
Since mtcars is a widely used statistic sample data, we don't do much description here. First plot the data mpg vs am (0 is automatic). Black dots are automatic

In figure 1 and Result 1, we can see manual cars have better performance than auto transmission cars (about 7 mpg better than auto), now let's see the confidence interval of the coefficients.

From Result 2, It's almost sure manual outcomes auto in mpg (3.6~10.8 for 95% confidence interval!).

##Doubt
Another thing is: let's plot the residual in figure 2 in appendix.

Seems not random distributed, which does not seem good...So let's add some more variables to it.

##Add Additional regressors
By intuition, we think Displacement, Number of Cylinders and Weight may have great effect to mpg. So we do 3 more regressions.

Refer to Result 3 for the three more regressions.

We could be able to see, as we increase the variable, the Pvalue for transmission type become very large, which means we could think transmission type has no effect on mpg!

##Analyze these additional regressors
Further more, we do anova on these fits, it's in Result 4

By looking at P-value for these linear regressions, none of the P-value is greater than 0.05, which means we fail to reject there is no connection between mpg and these added variables.

We plot the residual after adjustment of these variables, to see what it look like in figure 3.

Looks fine now!

Finally, we check the confidence interval for fit4 which considers all 4 variables, result is in Result 5 

Cosiders the P-value for fit4 we've done before, we might think mpg is more related to Number of cylinders and weight of the car.

##Conclusion
Based on the analysis above, we could get the inference:

* It's safe to reject the hypothesis that transmission type has impact on vehicles' mpg performance.
* The reason at the beginning, manual transmission has better mpg than auto is because the manual cars listed in the data tend to have more cylinders and heavy weight.
* Based on analysis, vehicles mpg may rely on other factors, such as Number of cylinders, displacement, weight, we don't do further analysis on this since it is out of interest.

##Appendix
Figure 1: initial plot
```{r,fig.height=3,fig.width=3}
library(ggplot2)
ggplot(mtcars,aes(am,mpg))+geom_point(color=mtcars$am+1,size=4)
```


Result 1: coefficient of basic fit
```{r}
fit<-lm(mpg~am,data=mtcars)
coef(fit)
```


Result 2: confidence interval of coefficient in basic fit
```{r}
confint(fit)
```


Figure 2: residual plot for basic fit
```{r,fig.height=3,fig.width=5}
qplot(mtcars$mpg,as.numeric(resid(fit)),color=mtcars$am,size=3)
```


Result 3: summary about coefficient for the three regressions.
```{r}
fit2<-lm(mpg~disp+am,data=mtcars)
fit3<-lm(mpg~disp+cyl+am,data=mtcars)
fit4<-lm(mpg~disp+cyl+wt+am,data=mtcars)
summary(fit2)$coef
summary(fit3)$coef
summary(fit4)$coef
```


Result 4: anova analysis on all the four regressions.
```{r}
anova(fit, fit2, fit3,fit4)
```


Figure 3: residual plot on fit4
```{r,fig.height=3,fig.width=5}
qplot(mtcars$mpg,as.numeric(resid(fit4)),color=mtcars$am,size=3)
```


Result 5: confidence interval of coefficient for fit4
```{r}
confint(fit4)
```